---
title: "Some Thoughts on Data Science"
format: html
editor: visual
---

## What do you think being a data scientist is about?

Personally, I think that being a data scientist is about the way you apply your work. In data science, a lot of the fundamental processes that are used are based on a foundation in statistics. The key distinction for me is the fact that data science is more concerned with the application of statistics to derive insight on data.

## What differences/similarities do you see between data scientists and statisticians?

Some key similarities:

-   Strong foundation in mathematical statistics

-   Using models/visualizations on data to derive insight from a set of observations

-   A variety of different industries utilize these professions in decision-making

A few differences:

-   Data scientists are more likely to work on big datasets, whereas statisticians will do more work on smaller datasets.

-   Statisticians tend to specialize in research and similar fields, whereas data scientists end up in a wide variety of professional roles.

-   A statistician is more likely to be working with more advanced statistical techniques, whereas a data scientist is more likely to work in an interdisciplinary manner by integrating aspects of software engineering and computer science into their work.

## How do you view yourself in relation to these two areas?

In my time at NCSU, I have found myself drawn towards my mathematical statistics classes the most. I definitely feel that being a statistician would resonate the most for me in terms of my interest in statistics, but I would certainly never turn down an opportunity to work as a data scientist if the industry/application of my work was of interest to me!

## A quick look at some petal widths

Using a pre-loaded dataset, let's take a look at some basic R functions:

```{r}

# Create a density function using petal widths from the iris dataset
y <- density(iris$Petal.Width)
```

We've now loaded the `y` object, let's take a look at some key characteristics of the object.

```{r}

#Get the class type
class(y)

#Get the internal type
typeof(y)

#Get the object structure
str(y)
```

Now, let's plot that density curve!

```{r}
#| echo: FALSE

#Plot the density curve we obtained earlier
plot(y)
```
